``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)

### 2022-12-23 paper/06--evaluation.tex
captions, ref, etc

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.

@@

While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)

>>>>

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in [blank] increase/decrease/similar, coverage and IPC score.

@@

While simple linearization can linearize almost none of the actually partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)

### 2022-12-23 paper/07--relatedWork.tex
captions, ref, etc

\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
of actions has an executable linearization. Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions. That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time. It can also find a executable linearization for that subset in polynomial time.

@@

The paper by \shortCite{DeleteRelaxation,Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.

>>>>

\cite{Erol1996HTNComplexity} proved that it is NP-complete to decide whether a partially ordered set
of actions has an executable linearization. Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions. That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time. It can also find a executable linearization for that subset in polynomial time.

@@

The paper by \shortCite{DeleteRelaxation,Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{Erol1996HTNComplexity}'s result (deciding whether a partially ordered
set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
